Indoor Dining Shutdowns Negatively Affect Toronto Restaurants’ Performance and Business Practices

### 2021-02-27 outputs/paper/paper.Rmd
Edited more spelling and grammar issues

Table \@ref(tab:Q5Q6tTest) displays changes in the numbers of employees working at restaurants in the sample prior to the intervention period (Oct 1) and following the intervention period (Dec 31). This shows us that initially, both the control and treatment group had a very similar number of employees on average. Following the intervention period, however, the treatment group appears to have 10.26 fewer employees on average. Two-tailed Welch's t-tests comparing the two groups' mean employees shows that the difference prior to the intervention period is not a significant finding \newline(*t*(330) = -8.56, *p* > .05), but the difference in employee numbers between the two groups post-intervention is significant(*t*(330) = 19.46, *p* < .05).

@@

# Output data table
t_tests %>%
  kable(
    booktabs = T,
    caption = "Welch's T-test to examine effects of intervention on the number of employees",
    digits = 3,
    col.names = c("Mean Difference",
                  "Mean (Pre-Intervention)",
                  "Mean (Post-Intervention)",
                  "t",
                  "p",
                  "df")

  ) %>%
  add_header_above(c(" ", "Control" = 1, "Treated" = 1, " ", " ", " ")) %>%
  kable_styling(full_width = F, latex_options = "HOLD_position") 
```

>>>>

Table \@ref(tab:Q5Q6tTest) displays changes in the numbers of employees working at restaurants in the sample prior to the intervention period (Oct 1) and following the intervention period (Dec 31). This shows us that initially, both the control and treatment group had a very similar number of employees on average. Following the intervention period, however, the treatment group appears to have 10.26 fewer employees on average. Two-tailed Welch's t-tests comparing the two groups' mean employees shows that the difference prior to the intervention period is not a significant finding \newline(*t*(330) = -8.56, *p* > .05), but the difference in employee numbers between the two groups post-intervention is significant(*t*(330) = 19.46, *p* < .05). This suggests shutting down indoor dining resulted in restaurants having to either let go employees, or employees chose to leave. These results do not indicate the position of the employees who were no longer at the restaurant at the end of the intervention, but we might assume many of the employees who left the restaurant during the study period were customer facing staff, such as waiters, whose full services were no longer required after indoor dining was shutdown.

@@

# Output data table
t_tests %>%
  kable(
    booktabs = T,
    caption = "T-test Results Measuring Effects of the Intervention on Number of Employees",
    digits = 3,
    col.names = c("Mean Difference",
                  "Mean (Pre-Intervention)",
                  "Mean (Post-Intervention)",
                  "t",
                  "p",
                  "df")

  ) %>%
  add_header_above(c(" ", "Control" = 1, "Intervention" = 1, " ", " ", " ")) %>%
  kable_styling(full_width = F, latex_options = "HOLD_position") 
```
